The GALEX View of ``Boyajian's Star''

### 2017-07-27 paper/paper.tex
compile first paper outline

\shorttitle{Rotating Stars}
\shortauthors{Davenport}

\author{
	James R. A. Davenport\altaffilmark{1,2}
	Riley W. Clarke\altaffilmark{1}
	Zachery Laycock\altaffilmark{1}
	Kevin R. Covey\altaffilmark{1}
	scott flemming\altaffilmark{3}
	tabby boyajian\altaffilmark{4}
	Bernie Shiao\altaffilmark{3}
	chase million\altaffilmark{5}
	ben montet\altaffilmark{6}
	david wilson\altaffilmark{7}
	Manuel Olmedo\altaffilmark{8}
	eric mamajek\altaffilmark{9}
	}

>>>>

\shorttitle{GALEX View of ``Boyajian's Star''}
\shortauthors{Davenport}

\author{
	James R. A. Davenport\altaffilmark{1,2}
	Riley W. Clarke\altaffilmark{1}
	Zachery Laycock\altaffilmark{1}
	Kevin R. Covey\altaffilmark{1}
	scott flemming\altaffilmark{3}
	tabby boyajian\altaffilmark{4}
	Bernie Shiao\altaffilmark{3}
	chase million\altaffilmark{5}
	Benjamin T. Montet\altaffilmark{6}
	david wilson\altaffilmark{7}
	Manuel Olmedo\altaffilmark{8}
	eric mamajek\altaffilmark{9}
	}
